\documentclass[12pt]{scrartcl}


\usepackage{epsfig,amssymb}

\usepackage{xcolor}
\usepackage{graphicx}
\usepackage{epstopdf}
\usepackage{multirow}

\definecolor{darkred}{rgb}{0.5,0,0}
\definecolor{darkgreen}{rgb}{0,0.5,0}
\usepackage{hyperref}
\hypersetup{
  letterpaper,
  colorlinks,
  linkcolor=red,
  citecolor=darkgreen,
  menucolor=darkred,
  urlcolor=blue,
  pdfpagemode=none,
  pdftitle={TITLE},
  pdfauthor={Christopher M. Bourke},
  pdfcreator={$ $Id: cv-us.tex,v 1.28 2009/01/01 00:00:00 cbourke Exp $ $},
  pdfsubject={PhD Thesis},
  pdfkeywords={}
}

\usepackage{fullpage}
\usepackage{tikz}
\pagestyle{empty} %
\usepackage{subfigure}

\definecolor{MyDarkBlue}{rgb}{0,0.08,0.45}
\definecolor{MyDarkRed}{rgb}{0.45,0.08,0}
\definecolor{MyDarkGreen}{rgb}{0.08,0.45,0.08}

\definecolor{mintedBackground}{rgb}{0.95,0.95,0.95}
\definecolor{mintedInlineBackground}{rgb}{.90,.90,1}

\usepackage[newfloat=true]{minted}

\setminted{mathescape,
           linenos,
           autogobble,
           frame=none,
           framesep=2mm,
           framerule=0.4pt,
           %label=foo,
           xleftmargin=2em,
           xrightmargin=0em,
           %startinline=true,  %PHP only, allow it to omit the PHP Tags *** with this option, variables using dollar sign in comments are treated as latex math
           numbersep=10pt, %gap between line numbers and start of line
           style=default} %syntax highlighting style, default is "default"

\setmintedinline{bgcolor={mintedBackground}}
%doesn't work with the above workaround:
\setminted{bgcolor={mintedBackground}}
\setminted[text]{bgcolor={mintedBackground},linenos=false,autogobble,xleftmargin=1em}
%\setminted[php]{bgcolor=mintedBackgroundPHP} %startinline=True}
\SetupFloatingEnvironment{listing}{name=Code Sample}
\SetupFloatingEnvironment{listing}{listname=List of Code Samples}

\setlength{\parindent}{0pt} %
\setlength{\parskip}{.25cm}
\newcommand{\comment}[1]{}

\usepackage{amsmath}
\usepackage{algorithm2e}
\SetKwInOut{Input}{input}
\SetKwInOut{Output}{output}
%NOTE: you can embed algorithms in solutions, but they cannot be floating objects; use [H] to make them non-floats

\usepackage{lastpage}

%\usepackage{titling}
\usepackage{fancyhdr}
\renewcommand*{\titlepagestyle}{fancy}
\pagestyle{fancy}
%\renewcommand*{\titlepagestyle}{fancy}
%\fancyhf{}
%\rhead{Computer Science I}
%\lhead{Guides and tutorials}
\renewcommand{\headrulewidth}{0.0pt}
\renewcommand{\footrulewidth}{0.4pt}

\lhead{~}
\chead{~}
\rhead{~}
\lfoot{\Title}
\cfoot{~}
\rfoot{\thepage\ / \pageref*{LastPage}}

\makeatletter
\title{Academic Integrity \& Code Usage Guidelines}\let\Title\@title
\subtitle{Computer Science I\\
{\small
\vskip1cm
Department of Computer Science \& Engineering \\
University of Nebraska--Lincoln}
\vskip-1cm}
%\author{Dr.\ Chris Bourke}
\date{Fall 2018}
\makeatother

\begin{document}

\maketitle

\hrule


\section*{Acceptable Usage}

\begin{itemize}
  \item Any function provided as part of a language's standard library
  \item Any piece of code that was provided to you by the instructor
  \item Any piece of code that you wrote as part of a lab, hack session or from another assignment
  \item Any piece of code \emph{you} wrote outside of class or for another class
  %\item Sharing your code with others \emph{after all possible due dates have passed} in order to learn and understand may be acceptable
\end{itemize}

\section*{Unacceptable Usage}

\begin{itemize}
  \item Any piece of code copied (in any form, cut-and-paste of any part, copying entire files or transcribing or reproducing code you saw from another student's copy
  \item Providing code to another student or allowing another student to copy your code or not taking reasonable measures to prevent another student from gaining access to your code
  \item Making your code publicly accessible prior to final grades posting
  \item Accessing sites such as:
  \begin{itemize}
    \item \url{http://www.chegg.com}
    \item \url{http://coursehero.com}
    \item \url{https://www.freelancer.com/} 
  \end{itemize}
  or anything similar will result in immediate failure of this course.  These
  are sites whose only purpose is to facilitate cheating and have no other 
  legitimate use as far as this course goes.
\end{itemize}

\section*{Don't Be Stupid}

It is \textbf{stupid to cheat} because:
\begin{itemize}
  \item You're not learning anything, you're wasting your money and your time 
  \item Your ignorance will eventually be exposed, either in your exams, future courses, or career; fail fast or fail slow.
\end{itemize}

It is stupid to \textbf{ask for or receive code from someone else} because
\begin{itemize}
  \item If you use it to any significant degree, it will be easily detected using MOSS.
  \item You undermine your own learning experience
  \item If they were willing to share it with you, they likely shared it with others, increasing nearly guaranteeing the likelihood that you will all get caught.
\end{itemize}

It is stupid to \textbf{give your code to someone else} because
\begin{itemize}
  \item They will likely end up screwing you by using it either in part or in whole which will easily be caught using MOSS.  You will suffer the consequences along with them.  You risk everything and gain nothing.
  \item They may share it with any number of other students, almost guaranteeing that you will all get caught.
\end{itemize}

It is stupid to \textbf{copy code off the internet} because
\begin{itemize}
  \item Your instructor can use Google too, you know.  We can just as easily find the source of your plagiarism and in fact can do it easier because we have your copy!
  \item Several other idiots may have the exact same bright idea!  Multiple students copying from the same source is going to be at the top of our red flag list when we run MOSS.
\end{itemize}

\newpage
\section*{Academic Integrity Testimonials}

\begin{quote}
``Computer Science is a course that requires a lot of extra time, it is comparable to learning a new language. As with every course taken from any school, you will get out exactly what you put into it. This is very true when an assignment calls for you to write your own, original code. Cheating or copying code is not the way to learn any new material, not only is an easy escape to class assignment, but will also leave you helpless when it comes to exams and labs, and eventually in the real world. Cheating also shatters any integrity you had, as a syllabus and course contract was signed saying not to cheat, and to be honest with all of the work submitted. As tempting as it is to just copy and paste, even on this one assignment, I highly encourage the reader not to. There are so many alternatives offered by the instructor and college, there is not a good reason to cheat. There are online discussion boards available, extensive office hours from the teachers assistants, graduate teaching assistants, and instructors. A lot of these people are more than willing to help with any questions you may have, and make it very easy to come in and get the help you need. Another great resource is to look back at course slides, notes, and lab work. A lot of this work was demonstrated either in lecture notes, or done in lab with help from fellow classmates and teaching assistants. The instructors and teaching assistants also make it easy to revisit this material.  With all of these options, you are not completely left to your own devices, and there are a fair amount of people who want to help, and there are plenty of resources to look to instead of copying from the internet, or copying off of friends or classmates. In conclusion, I highly suggest putting the time and effort into learning how to use the resources made readily accessible, and not relying on the internet to get assignments done.'' \end{quote}

\begin{quote}
``Nothing is worth risking your future and your reputation. You are a good student and a hard worker, but you need to make time and plan ahead for your classes and assignments. Yeah you are overwhelmed with your schedule this year, but there is no excuse for cheating or getting behind. You have plenty of time to re-read lecture notes and practice labs. You need to split focus up equally between classes. It is so pointless to cheat just to get by in a class, because you know deep down you are going to constantly think about the fact you didn't do it on your own, you didn't do it the right way. It will constantly eat at you knowing that you cheated to get the grade you have, when you know if you worked hard enough, you could do even better. And again, if you got caught? You're screwed. You could fail the course or assignment, or even worse. No stupidity or cheating is worth that price of letting your friends and family down. You strive to make your parents proud every day, and this cheating could destroy them and what they think of you. Nothing is worth that. Especially after they have given you all the tools to be successful, do not throw that away. You may be panicking now, but that is because you have not organized your schedule to make time for studying and preparing for every class. Yes this class may get hard at times, but just remember that feeling of gratitude when you finally understand the programming and you start to enjoy coding because you actually know how to use and manipulate code. There was no reason to get behind or late on this assignment, and there was definitely no reason to cheat. You can understand and get an amazing grade by studying and working hard for your grade so you can feel accomplished and deserving of that grade at the end of the semester. You are so much better than this and you can work so much harder and apply that to real life and every other class you are in. Let this message guide you to the right path in being successful and never let cheating be a thought in your mind ever again. Work your hardest and prove to everyone how great you can be with hard work and dedication.''\end{quote}

\begin{quote}
``In order to help future students with mistakes that may affect their path I have two messages. First, be careful with handing out your code to people. While you may do so with good intentions hoping to help somebody, it may come back around to hurt you. Second, make sure to start all of your homework early. If you are diligent with your work, then you will not be going to the resource center the day homework is due and you will not be seeking other students for help, which might lead to a bad decision.''
\end{quote}

\begin{quote}
``On one of our assignments, I asked a student to share one of his programs with mebecause I waited until three days before it was due to start on it. Put simply, I panicked and saw cheating as the only way I could finish the assignment in time. I learned the hard way that when the instructor says they'll catch any cheaters, they most definitely will catch them. In hindsight there were many other options I had, such as starting the assignment while we were covering the material in lecture as opposed to doing it two weeks later. I've never been the type of person to cheat on assignments or tests since I think it's counterproductive and devalues the effort of people who actually did the work. It's wrong for me to get credit for something I put no work into. If I could do it over, I would've just done whatever I could with the time I had and turned it in, even if it wasn't finished.''
\end{quote}

\begin{quote}
``I am writing this paper because I had a program that matched very closely with several other students. The intent was not to cheat, but to instead help someone out. This guy needed some help on a program that I had already completed, and he had helped me out with a problem I was having on another part of the assignment, so I figured why not help him. So, I ended up just sending him my code and he pretty much copied the whole thing word for word.  Not only did he copy it, but he then sent it to more people and they all copied it pretty much word for word. 	I would highly recommend not to cheat because in the end it's not worth it at all. Eventually, with all the technology that the university has, you will be caught and maybe the professor will be in a bad mood that day and will just kick you out of the class. Then your parents are mad because they just threw money down the drain for that class and now there are even more consequences. So, just struggle through the assignment and actually learn something that you may be able to apply in the future.''
\end{quote}

\begin{quote}
As a general rule of thumb, if the thought goes through your mind that this could possible qualify as cheating, it more than likely is. Even if it doesn't cross your mind that what you're doing could be cheating, it still might be. There was one particular assignment that a lot of people were struggling on, so me and my partner started talking to someone else we knew in the class and just asking things like, "Hey, how did you get this to work?" And "Is this how this is supposed to be?" Then one thing led to another and my partner and I ended up sending the other individual our code so they could physically look at it and see what was working for us. Looking back this was definitely a red flag, but we didn't really think of it as that at the time. It is easy and convenient to go to your fellow classmates and discuss an assignment and get some help, but what we did was a step too far. Dr. Bourke is generous enough to let us work with a partner and that is not something we should push the boundaries of and take advantage of. My partner and I were very lucky that we did not receive a harsher punishment. The University does not take lightly to cheating and has a near zero tolerance policy, so just don't do it. Whenever you cheat you risk expulsion, and that is not something you want to toy around with.My advice to you would be to take advantage of the resource center and of office hours. It is amazing how much Dr. Bourke and the TA's know about programming in C, I can almost guarantee that they can help you more than anyone in the class can. Also, be proactive with going into office hours. If you wait until the Friday that the assignment is due you'll spend most
of your time waiting for a TA to get done helping all the other people that put it off before you can get helped.
\end{quote}

\begin{quote}
``I know that right now you think that there is a million other things you would rather do than start on your programming for CSCE 155E, but you need to begin working on that assignment now. Most of the semester you have been able to get a majority of your assignments done relatively quickly with help in the resource center from a TA, but you will benefit much more starting it now. There are many different reasons that starting early on your assignments can prove to be more beneficial for you in this class and in all your school work for this semester. 	The first reason is that it may cause you some struggling early on while starting the assignment, but it will save you tons of stress in the near future. If you ask for help from a TA with a program that already has a majority of it finished, you will be able to get more direct help on the program. This will also restrict your questions and allow time to be spent more usefully for you and the TA. If you can do this, you will cause less stress for you as you approach the deadline for the assignment. 	Another reason to begin earlier is that if you can learn and adapt your program by yourself you will gain much more from this assignment. CSCE 155E is no simple class and the more you can learn from assignments by yourself without assistance the more able you will be to understand your midterm and final exams. Being able to understand the basic concepts and lessons that are outlined on each code throughout the semester will appear on those exams. 	One final reason is that you will gain more knowledge out of this course. As a mechanical engineer you may not think that this course is not as important to your field as much as some other classes. However, having the knowledge of being able to understand the basics of programming in a language in C can provide very valuable skills for your future. This class may help spark a new interest in you to possibly become more interested in computer science. It can also help you understand the basic principles behind many different things that happen within our regular technology use everyday. This knowledge can also provide a deeper understanding with the computer science field as you enter the work force, making you much more well rounded and able to communicate with them in situations.	All in all, you should start much earlier on you CSCE 155E homework assignment to prevent stress, be more prepared for exams, and obtain more from the course. It will also help you in upholding your personal character and integrity before you are put in a position worrying about being able to finish the assignment on time. Being in this position can and will lead you and many others to try and lazily manipulate another student's code instead of working on your own.''\end{quote}

\begin{quote}
Towards the end of the semester, my partner and I submitted code for a homework assignment, that ended up being flagged as plagiarized. It was the result of a wide variety of factors; other class conflicts, non-academic commitments, and poor time management, to name a few. To help you all best understand my situation, I will start the beginning, to prove the point that no matter the situation or circumstance, you should never follow in my footsteps.	I want to preface my story by saying that your professors were students once as well; they know what college can be like for some people. They fully grasp the notion that people have other things going on outside of their work for their specific course. With that being said, I'll skip past a lot of the personal details as to how we got to where we were, but it was about 5 hours before an assignment was due on Friday night. I had just gotten back to my room for the night, and went to work on finishing my assignment with my partner. For me at least, this week had been the most busy week I have had since starting college, it felt as though I never had a minute to breathe. All we had completed at the time was part 1 (of 3) for the assignment. Before that night, we hadn't had hardly any time to come together to work on the assignment. But like I said, that doesn't really matter, deadlines are deadlines. 	We sat down to start part 2 and 3, read over them a few times, and we knew what we needed to do, but didn't know exactly how to structure it in physical code to accomplish what we wanted. So we began searching through what lecture notes and old lab code we could find, and didn't find anything that really fell in line with what we needed to do. By this time, we only had a little over 2 hours remaining before the deadline. So we did the only other thing we could think to do in that situation, by taking to the internet to try to find out how to structure what we wanted to do. A little more searching, and I found something that I thought would work for what we wanted, so I began using that as a reference to build our code off of. Another hour or so later, I had thrown together some code but was struggling to get the results we wanted, and time was running out. We had thrown together some code that half worked for part 3 by then as well, and continued to work until we had about 20 min left, and had made no significant progress, as we changed the code from part 2 to work the same way as what we had found online, changed things here and there, and turned in the assignment just before it was considered late. 	Turns out, our submission got flagged for plagiarism, which violates thew CSCE academic integrity policy. When I heard the news, I panicked, I felt like my life was over, that I was getting kicked out of college, my extracurriculars, everything--all gone because I made a single boneheaded mistake. In my head, I knew what I was doing was wrong, but in my head at the time, I saw no other option. Oh how wrong I was, fortunately for me, my professor cut me and my partner a huge break, by giving us the choice to take a zero for the entire assignment, or to take a zero for the section that was plagiarized, and for me to write this for you all. Make no mistake, I am not doing this just because I have to. I am doing this because I feel genuine remorse for what I did, from the moment I submitted it, and I want to do everything in my power to do right by it. So the solution was to share my experiences in order to keep people from making my mistakes. 	My advice to anyone who finds themselves in a situation where they will not have time to work on the assignment until just before its due, plan ahead, find time to do it well in advance, in case something comes up. If you do that and determine you will not be able to finish something like a week ahead of time, talk to your professor, see if they will work with you. If not, then you will have to prioritize as well as possible. At the end of the day, it is better to turn in partially completed work then to try to use someone else's They will find out, and they will enforce the consequences.\end{quote}

\begin{quote}
	While Completing an assignment for our Computer Science I class, me and my partner turned in a program which was almost entirely plagiarized from the internet.  I personally was not aware of this, but that does not mean I am any less at fault.  The most basic reason why this happened was that we did not start the assignment in time.  We procrastinated to the point where we started the assignment on the day which it was due.  For this particular program, I did not understand one of the main aspects of it, and so I let my partner do most of the work.  I provided help where I could, but was not as involved as I should have been.  As it turned out, my partner understood the program because he took the majority of it from a program online designed to do the same thing.  This program turned up with a 98\% match to the program found online, and we were informed that we had been caught for plagiarism.	Although I did not know of or participate in the copying of code, I was still equally responsible for the situation.  The Professor had a specific way which partners were supposed to work together, but because I did not understand the material, I could not participate as I should have.  Had I understood the material and been as involved as I should have been, the situation could have been avoided.  A Program with two authors should have equal participation from both authors.  Even if there are parts of the program which you did not contribute to, you are 100\% responsible for every line of code in a program which bears your name.  My partner may have been the one to actually copy and paste code, but it was my responsibility to be involved in every step of the process.  Whenever you turn in an assignment, be sure that you and your partner both put equal effort into each program and understand and approve of every line of code.	Plagiarism when it comes to any academic work is not acceptable and will be caught.  If any assignment of yours is caught for plagiarism or any other type of cheating, you bear 100\% responsibility for that violation of academic integrity.  UNL and every other university takes cheating very seriously.  If any person is able to get away with cheating, it is not only unfair to the other students in the course, but can bring into question the integrity of the program itself.  You are responsible for upholding the integrity of the University and of the College, and if you fail to do so, they will take action to ensure that the course remains fair for all students involved and that the program remains credible.  This can mean something such as a warning or probation for a minor violation, up to a suspension or even expulsion for major violations.  Cheating is morally wrong, academically dishonest, and hurts not only you, but your classmates, the college, and the University.	Computer Science is a very time intensive field.  In order to do each assignment properly, you need to put in the time and effort required.  Never put an assignment off until the last minute.  The best case outcome is that you are able to turn in a working but shoddy and rushed program.  The worst case is that you cannot turn in a working program, or you cheat, which will be caught.  Even If you are completely lost on an assignment, the professor and TA's can and will help you get to a point where you can write a proper program, but you need to use your time wisely in order to realize that you do not understand something, got to a TA to learn what the issue is, and implement a proper fix.  If you put in the proper time, you can get an A on every homework assignment.  If you did procrastinate, do what you can properly, and accept that your grade may not be what you would like.  At that point it is usually too late to reach out for help.  Copying code from the internet or from a friend will be caught every time, and you will not only receive a worse grade than you would have if you had only turned in what you personally could write, but you will also face whatever additional punishment the professor, college, and university deem necessary.  There is absolutely no upside to cheating, and you will not get away with it.  Again, if you are in a position where you are not going to be able to complete an assignment, accept that you made a mistake, and fix your habits for the next assignment.  The very best way for you to avoid a situation like mine is to allocate enough time for each assignment, remain involved in every line of code which you or your partner writes, and accept mistakes you make and fix them for the future.  One bad grade on an assignment will not automatically destroy your grade, but, by cheating, you open yourself up to receiving absolutely no credit for the assignment, or immediately failing the class.  I was lucky to only have credit taken away for the plagiarized program.  Please learn from my mistake and avoid any situation which may lead to cheating.\end{quote}
	
\begin{quote}
In computer science classes, it's important to get a head start on every assignment and to get as much approved help as possible.  The classes are hard, and the assignments require a lot of work and attention.  In my situation, I was working on an assignment that a lot of other students were having trouble with, including myself.  I was going into the Resource Center a lot the week and two before it was due getting help from TA's.  However, since a lot of other students were having difficulties with the assignment, the SRC was busy and so were the TA's.  It had gotten to the last two days to be able to work on the assignment and I had still not gotten any farther with my assignment.  While waiting in line for a TA to look over my code and help me, another student in line mentioned how he found something online that was a correct solution for my problem in the assignment.  I then looked it up and used the code to see if it worked.  I noticed it worked and then copied parts of it into my assignment because I was frustrated with not being able to figure it out myself or with the help of the TA's.	At the time I knew what I was doing wasn't right, but I was frustrated and had spent a lot of time on the assignment and thought a lot of other people might've done the same thing.  I knew that the other student had used it and that it was easy to find online if other students were having the same struggles.  No matter what situation you're in, copying and cheating does not and will not make it better.  Just like a paper or essay for an English class, social studies class, etc., it's wrong to copy someone else's work and ideas.  In math and science classes, there's pretty much only one way to do a solution which is close to what programming problems are like.  There are still multiple ways to do a programming assignment.  In addition, it still does not make it right to copy someone else's work while you do none of the actual work.  You also don't truly learn and apply yourself when you copy from someone online or in person.  After turning the assignment in, I regretted what I had done and wished I could go back and try to figure the problem out myself more because I knew what I did was wrong and there would be consequences.  Before doing anything, you should evaluate yourself and make sure you are thinking clearly and making no mistakes that you'll later regret.	To all current CS students or future CS students, always get ahead on an assignment and use approved resources to the fullest.  Compared to high school, college classes are a lot harder and require a lot more work, especially computer science and programming classes.  If you're struggling with an assignment and find something online that will work, it's not worth it to copy and cheat.  From my experiences, I know that it is not worth the risk and consequences to cheat and copy.  It's also morally and ethically wrong.  If you get caught cheating, you risk getting a 0 on the assignment or an F in the class which compares nothing to just trying to figure it out yourself and getting a ``bad'' grade on the assignment if you can't end up figuring it out.  Computer science and programming classes are hard which means you're meant to struggle with it.  It doesn't make it okay to cheat and use code from another student or from an online source.
\end{quote}

\begin{quote}
It was around 8:00, and I was starting to work on the second program for assignment five. I had spent the past couple of hours on the first program, and despite the segmentation fault I was trying to work out, I figured a better use of my time would be to start working on the other programs for the assignment rather than fixating on a bug. I started to work out on pen and paper how I was going to go about things. I thought that I might be able to modify some of the functions I had already written on assignment four, but I didn't have much success. While we weren't working as partners, I was working alongside someone who was working on the same assignment. In the midst of my thinking process, he had pulled up a GitHub page on my computer, which had the code for a sudoku Verifier, nearly identical to the task in assignment five. I looked at the code on the webpage and figured that it was better than anything that I was going to come up with in the dwindling time I had left.	While writing the program, I did my best not to copy the GitHub post directly, changing variable names and only taking some of the main elements of the program. At the time, it didn't fully register in my mind that I was plagiarizing something because I was more focused on having something to turn in rather than the quality of what I was turning in. It took some time to get the program to compile without any errors and run, however it didn't work as it should have. I spent another few hours trying to get it to function properly, but couldn't figure it out, all the while looking back to the GitHub post more and more to reference how it was implemented there, and how I could adapt what I took to work in this situation. Ultimately, I never got the program to work, and left myself with a few minutes to write the DNA mutator program, which also ended up being filled with errors and not working due to the short amount of time I tried to complete it in. I managed to get all three programs turned in, albeit none of them working, just minutes before the 11:59 P.M. deadline. 	When I woke up the next morning and checked my phone, I saw an email from Piazza that Professor Bourke made a new post: Cheating. Without even opening the email, my heart sank. I was too caught up in meeting the deadline that I didn't realize I was plagiarizing something. Before now, I've never plagiarized anything. Driving to and from Omaha to see my family, all I could think is ``I'm a cheater'' and that I could get expelled. I felt terrible, and all I could think to do was to be honest with what I had done. I went to Professor Bourke's office hours on Monday and turned myself in, and when I did it felt like a huge weight was lifted off of my shoulders. 	I learned my lesson. I procrastinated too long before starting the assignment and was so caught up in finishing it on time that I resorted to doing something immoral, and I didn't end up with any working programs anyways. Cheating is never worth it.
\end{quote}

\begin{quote}
Plagiarism is something I'm sure everyone has heard of. It's the act of copying another's work and claiming it as your own. It can be displayed in many different ways, and sometimes it may not even seem like you are plagiarizing when you are. Many people consider plagiarism as only the act of copying someone's program word for word, but that's not the only way plagiarism is defined as. I will explain what I did wrong, why I did what I did, and why it is wrong from my point of view.In my case, I had significant troubles coding my program. I continued to fall behind in class due to the fact that my mind doesn't think in the way a coder's mind does. As a Civil Engineering student, I enjoy working with water systems and autocad related programs. I have always had a problem understanding the way code is and how it works. In my situation, I was trying to make my first and third problem for this three-part assignment as good as I could as I was told that the sudoku verifier was the easiest, but when I had started coding it I got so lost. I thought the best solution for this would be to go to the resource center and get some help. This, however, was where I did not make the best of decisions.At the resource center, I asked a fellow student for help with this particular question as every method I had tried did not work. What I ended up doing is while getting help was when asking a fellow student for help, he ended up helping me and giving me almost exactly what he had for his personal code. This is where I went wrong. I should have known that it was going to be too similar and redone it since I relatively understood the concept of what I was to do, but  I was crunched for time as it was Friday night and ended up leaving that to be my submission. After looking back at it I know what I did was wrong and that I should have trusted my gut in fixing with a better version that I personally had done completely. In the end it is what it is, and I can't do anything else about it other than not do it again. It is something I would highly recommend against doing as it can hurt a reputation severely, and cause something worse than just hurt your grade.\end{quote}

\begin{quote}
This paper should be a reminder about situations where collaboration happens and the consequences that happen because of collaboration. In my situation, it did violate academic policies and it's not worth the risk. I'll talk about my situation, why I did it, and why it was wrong. Take this paper as advice as I can tell what to do to avoid plagiarism and really, think twice about what you're putting yourself into.For the assignment I was working on, it about strings and implementing functions with strings. First of all, make sure you know what you're doing before an assignment because it will save you time to actually know how to implement a function instead of being lost. I did work on a part of the assignment but I had problems such as segmentation faults in which I did not know how to fix. I could have let these problems be but I also wanted a good grade on this assignment so I decided to seek for help. Working in the computer resource room, I met with a classmate that had similar problems. Luckily for him, he had a copy of a solution that he got from his friend. I wanted to get rid of the errors I had so I asked if I can work on the part of the assignment with him. I already had a partner and collaborating with this classmate would have been in violation of the academic policies. To be honest, I am not the best at C programming and being able to get a good grade on this assignment seemed far from reality so I decided to work with him. I was only thinking about how my grade can be saved if I were to use the code he had. I used a couple of function that the solution had to get rid of the segmentation faults as he did the same. Thinking that changing variable names and formatting would hide the fact that we had the same structure of code, I believed that I would not get caught with collaboration and get that good grade after all. Soon enough I was emailed about my code being similar to that same classmate. In the end, we ended up with similar code. We violated the rules. Only partners should work on code together and no one else. This is just one example of the many cases people have broken the policy. Although we collaborated, in another perspective, it can be considered plagiarism. I didn't realize the amount of trouble I was putting myself into until I was notified. You may think you are doing nothing wrong by copying a bit of code but even that small amount of code can create trouble. My advice I have to offer is get help when you are stuck. I must admit programming is hard so take the time to learn it. When you busy learning in other classes including computer science, you are not going to be able to know how to write all the code for the assignments. You can seek help by simply going to your professor. Professors have office hours so they have students come with questions and they will help. TAs are also another resource in case you can't make to your professor's hours and they are located in the computer resource room where it is accessible to everyone. Other than idea of receiving help so you can succeed, I think the consequences of cheating are bad enough to make you stay away from doing it. If you plagiarize, you will definitely not get a good grade on your assignment. So study the material enough, seek help when you need it, and plagiarism should not be anything you consider in your studies. This goes for classes other computer science. College is difficult but not impossible. There are enough resources and you have to give yourself enough time to work on your studies. Time is precious so don't start on your assignment late. Take this advice and you'll never have to worry about bad grades or getting in trouble.
\end{quote}

\begin{quote}
Contrary to popular belief of students, academic plagiarism is not a grey area. Plagiarism, or the deliberate use of another person's original work as one's own, is strictly forbidden at UNL and quite easy to detect. There is a university-wide policy against plagiarism, as well as a class policy created in an attempt to prevent academic dishonesty. In fact, the CSE department at UNL has written their own program designed to catch similarities in code submissions for every assignment that passes through its servers. Though you may think you won't be caught, you will be. It is not worth attempting plagiarism at any level: risking a failing grade, a zero on something worth 10\% of the entire class grade, or worse consequences is not worth the payoff of being able to submit an assignment you didn't learn yourself in a class you pay hundreds of dollars to take.	To make this message more realistic, I was caught with plagiarism. In CSCE155E in Bourke's class, six homework assignments comprise 60\% of the entire class grade. This means that each assignment is worth 10\% of your grade. Professor Bourke gives a generous two weeks to complete each assignment, and even gives a free ``late pass'' if two weeks isn't enough to complete the assignment. We are also allowed to work with one other person on each coding assignment. This may make the course seem easy to pass, but with these things going in your favor, the assignments are far from easy if you are unfamiliar with the C language. 	Though my partner and I worked for about 20 hours on our fifth assignment, we did not spend enough time learning the material necessary to understand how to correctly complete the assignment. We had our code written, but it did not work on the CSE server's webgrader that checks for correctness. We wrongly decided to collaborate with another student outside of our group, thinking we wouldn't get caught. Despite the clear instructions stating that ANY collaboration on code with a person not in your chosen group of two is forbidden, we decided to do it anyway.	We ran into another student in a physics class (not even 155e) and he let me take a picture of one function (of five) from one part of a three-part assignment to compare with my function that didn't work. I typed out his function and put it through webgrader under my name to check if his function worked and put my function under comments, so it would compile. When I turned in my assignment, his code remained on my program, and I was caught almost instantly, before the grades for the assignment were even released. I thought plagiarism wasn't that big of a deal before this, but after seeing how easy it is to get caught and what the consequences are compared to the empty payoff (you don't even learn what you're paying to learn), I've learned how stupid it is to try to use another person's code in your program. Moral of the story: please don't attempt to plagiarize. Especially if you have access to others' code, or a Chegg account. My partner and I were definitely not the only ones caught this semester, and I have a feeling we won't be the last. I implore whoever reads this to take my word for it: I was lucky to receive the penalty I did. Plagiarism, in any form, is NOT WORTH IT.\end{quote}

\end{document}
