\documentclass[12pt]{scrartcl}

\input{preamble}

\makeatletter
\title{Hack 12.0}\let\Title\@title
\subtitle{Computer Science I -- Java\\
Recursion \& Memoization\\
{\small
\vskip1cm
Department of Computer Science \& Engineering \\
University of Nebraska--Lincoln}
\vskip-3cm}
%\author{Dr.\ Chris Bourke}
\date{~}
\makeatother

\begin{document}

\maketitle

\hrule

\input{instructions.tex}

\section*{Problem Statement}

A binomial coefficient, ``$n$ choose $k$'' is a number that corresponds 
to the number of ways to \emph{choose} $k$ items from a set of $n$ distinct
items.  You may be familiar with some the notations, $C(n,k)$ or $C_n^k$ 
or ${}_{n}C_k $, but most commonly this is written as 
  $${n \choose k}$$
and read as ``$n$ choose $k$''.  There is an easy to compute formula involving
factorials:
  $${n \choose k} = \frac{n!}{(n-k)!k!}$$
For example, if we have $n = 4$ items, say $\{a, b, c, d\}$ and want to choose
$k=2$ of them, then there are 
  $${4 \choose 2} = \frac{4!}{(4-2)!2!} = 6$$
ways of doing this.  The six ways are:
  $$\{a, b\}, \{a, c\}, \{a, d\}, \{b, c\}, \{b, d\}, \{c, d\}$$
There are a lot of other interpretations and applications for binomial 
coefficients, but this hack will focus on computing their value using
a different formula, Pascal's Rule\footnote{Which can be used to generate
Pascal's Triangle, \url{https://en.wikipedia.org/wiki/Pascals_triangle}}:
  $${n \choose k} = {n-1 \choose k} + {n-1 \choose k-1}$$
which is a recursive formula.  The base cases for Pascal's Rule are when
$k = 0$ and $n = k$.  In both cases, the value is 1.  When $k = 0$, we are
not choosing any elements and so there is only one way of doing that (i.e.\
choose nothing).  When $n = k$ we are choosing every element, again there
is only one way of doing that.  

\subsection*{Writing a Naive Recursion}

Create a class named \mintinline{text}{Binomial} and implement and 
test the following method \emph{using a recursive} solution:

\mintinline{java}{public static long choose(int n, int k)}

which takes $n$ and $k$ and computes ${n\choose k}$ using Pascal's Rule.
Note that the return type is a \mintinline{java}{long} which is a 64-bit
integer allowing you to compute values up to 
  $$2^{63}-1 = 9,223,372,036,854,775,807$$
(a little over 9 quintillion).  Write a \mintinline{java}{main} method
that takes $n$ and $k$ as command line arguments and outputs the result
to the standard output so you can easily test it.

\subsection*{Benchmarking}

Run your program on values of $n, k$ in Table \ref{table:easyValues} 
and time (roughly) how long it takes your program to execute.  You
can check your solutions with an online tool such as 
\url{https://www.wolframalpha.com/}.

\begin{table}[ht]
\centering
\begin{tabular}{c|c}
$n$ & $k$ \\
\hline\hline
4 & 2 \\
10 & 5 \\
32 & 16 \\  %5 seconds
34 & 17 \\  %15 seconds
36 & 18 \\ %60 seconds
\end{tabular}
\caption{Test Values}
\label{table:easyValues}
\end{table}

Now formulate an estimate of how long your program would take to 
execute with larger values.  You can make a \emph{rough} estimate 
how many method calls are made using the binomial value itself.  
That is, to compute ${n \choose k}$ using Pascal's Rule would make 
\emph{about} ${n \choose k}$ method calls.

Use the running time of your program from the test values to 
estimate how long your program would run for the values in 
Table \ref{table:hardValues}.

\begin{table}[ht]
\centering
\begin{tabular}{c|r}
${n \choose k}$ &  value \\
\hline\hline
${54 \choose 27}$ & =     1,946,939,425,648,112 \\
${56 \choose 28}$ & =     7,648,690,600,760,440 \\
${58 \choose 29}$ & =    30,067,266,499,541,040 \\
${60 \choose 30}$ & =   118,264,581,564,861,424 \\
${62 \choose 31}$ & =   465,428,353,255,261,088 \\
${64 \choose 32}$ & = 1,832,624,140,942,590,534 \\
${66 \choose 33}$ & = 7,219,428,434,016,265,740 \\
\end{tabular}
\caption{Larger Values}
\label{table:hardValues}
\end{table}

\subsection*{Improving Performance with Memoization}

You'll now improve your program's performance using memoization
to avoid unnecessary repeated recursive calls.  

\begin{enumerate}
  \item First, change your return type to use Java's \mintinline{java}{BigInteger}
  class.  This is an arbitrary precision number class meaning that it can 
  represent arbitrarily large integer values.  You won't be able to use 
  the normal arithmetic operators however.  Instead, you'll need to RTM and
  use the class's methods to add and perform other operations.  See the
  documentation here: \url{https://docs.oracle.com/en/java/javase/14/docs/api/java.base/java/math/BigInteger.html}
  \item To ``cache'' values so that you are not continually repeating the
  same calculations over-and-over you \emph{could} use a table, but let's 
  use a \emph{smart data structure}: a \mintinline{java}{Map}.
  
  This map will be used to map a pair of input values, $(n,k)$ to the
  value of the binomial ${n \choose k}$.  The problem is that we want
  to use the combination of two values as a single key.  To do so, we've
  provided a \mintinline{java}{Pair} class that allows you to pair two
  objects together to use as a key.
  
  Create and instantiate a static map of the following type:
  
  \mintinline{java}{Map<Pair<Integer, Integer>, BigInteger>} 
  
  \item Modify your \mintinline{java}{binomial} method to use this map
  to store and use values to avoid unnecessary repeated recursive calls.
  Your method should have the following signature:
  
  \mintinline{java}{public static BigInteger binomial(int n, int k)}
  
  When the method needs to compute ${n \choose k}$ it checks the map
  first: if the value has already been computed (is not \mintinline{java}{null}) then it
  returns that value.  Otherwise, it performs the recursive computation.
  Before returning the value, however, it should store it (\emph{cache}
  it) in the map so that subsequent computations avoid the recursion.  
  
  \item Rerun your program with the values in Tables \ref{table:easyValues} 
  and \ref{table:hardValues} to verify they work and note the difference
  in running time.  
\end{enumerate}

\section*{Instructions}

\begin{itemize}

  \item All your code should be in the class file, 
  \mintinline{text}{Binomial.java} along with full documentation.

  \item You are encouraged to collaborate any number of students 
  before, during, and after your scheduled hack session.  

  \item Include the name(s) of everyone who worked together on
  this activity in your source file's header.

  \item Turn in all of your files via webhandin, making sure that 
  it runs and executes correctly in the webgrader.  Each individual 
  student will need to hand in their own copy and will receive 
  their own individual grade.
\end{itemize}  


\end{document}
