\documentclass[12pt]{scrartcl}

\input{preamble}

\makeatletter
\title{Hack 13.0}\let\Title\@title
\subtitle{Computer Science I -- Java\\
Searching \& Sorting\\
{\small
\vskip1cm
Department of Computer Science \& Engineering \\
University of Nebraska--Lincoln}
\vskip-3cm}
%\author{Dr.\ Chris Bourke}
\date{~}
\makeatother

\begin{document}

\maketitle

\hrule

\input{instructions.tex}

\section*{Problem Statement}

You will use the implementation of your \mintinline{java}{Airport} class 
from a previous hack to develop several reports that will require you to 
sort and search (a subset of) the International Civil Aviation Organization 
database for particular airports.  

We have provided a source file, \mintinline{text}{AirportUtils.java} with
several comparators and methods you need to implement.  Details are provided
in the documentation.  

The \mintinline{java}{generateReports()} takes a list of 
\mintinline{java}{Airport}s and should produce the
following reports which should all be output to the standard output.

\begin{itemize}
  \item To help you troubleshoot, you should print out the list of
  airports in the original order to the standard output.
  
  \item Sort the airports by each of the 8 comparators and print them 
  out (8 reports total).

  \item Search for and print out the airport in the array that is closest (via 
  air distance) to Lincoln.  Lincoln is located at 40.8507N, 96.7581W.

  \item Search for and print out the airport that is the geographic west-east
  median\footnote{With 0-indexed lists, the median is usually the element at
  index \mintinline{c}{n/2} when sorted.  This relies on truncation to give 
  the middle index of odd-sized lists and prefers the ``right'' element 
  for even-sized lists.} 
  of the given airports with respect to longitude.  
  
  \item Search for an airport located in the city New York (city would 
  be \mintinline{text}{New York} and the country would be 
  \mintinline{text}{US}) and print it out
  if it exists.  If no such airport exists, print out an appropriate message.
  
  \item Search for an airport whose type is \mintinline{text}{large_airport} and
  print it out if it exists.  If no such airport exists, print out an appropriate message.
\end{itemize}

\section*{Instructions}

\begin{itemize}

  \item Hand in both your \mintinline{text}{Airport.java} and 
  \mintinline{text}{AirportUtils.java} source files.  You may add any 
  utility methods you wish but you must \emph{not} change any of the 
  signatures of the required methods.
  
  \item In addition, you must create a \mintinline{java}{main} 
  method in your \mintinline{text}{AirportUtils.java} class that
  tests your reports with at least least 5 airports. 
  
  \item You are encouraged to collaborate any number of students 
  before, during, and after your scheduled hack session.  

  \item You may (in fact are encouraged) to define any additional
  ``helper'' methods that may help you.

  \item Include the name(s) of everyone who worked together on
  this activity in your source file's header.

  \item Turn in all of your files via webhandin, making sure that 
  it runs and executes correctly in the webgrader.  Each individual 
  student will need to hand in their own copy and will receive 
  their own individual grade.
\end{itemize}  


\end{document}
