\documentclass[12pt]{scrartcl}

\input{preamble}

\makeatletter
\title{Hack 2.0}\let\Title\@title
\subtitle{Computer Science I -- Honors\\
{\small
\vskip1cm
Department of Computer Science \& Engineering \\
University of Nebraska--Lincoln}
\vskip-1cm}
%\author{Dr.\ Chris Bourke}
\date{~}
\makeatother

\begin{document}

\maketitle

\hrule

\input{instructions.tex}

\section*{Problem Statement}

Consider two locations, an origin and a destination, on the globe 
identified by their latitude and longitude.  The distance between
these two locations can be computed using the Spherical Law of 
Cosines.  In particular, the distance $d$ is
 $$d = \arccos{(\sin(\varphi_1) \sin(\varphi_2) + \cos(\varphi_1) \cos(\varphi_2) \cos(\Delta) )} \cdot R$$
where
\begin{itemize}
  \item $\varphi_1$ is the latitude of location $A$, $\varphi_2$ is the latitude of location $B$
  \item $\Delta$ is the difference between location $B$'s longitude and location $A$'s longitude
  \item $R$ is the (average) radius of the earth, 6,371 kilometers
\end{itemize}

Write a program that \emph{prompts} the user to enter the latitude 
and longitude of two locations and then computes the distance between them using
the above formula.  Note that latitude inputs will be in degrees and in the
range $[-90, 90]$ and longitude will be in degrees in the range $[-180, 180]$.
Negative values correspond to the western and southern hemispheres.  

Note that the formula above assumes that latitude and longitude are 
measured in radians $r$, $-\pi \leq r \leq \pi$.  You can convert from
degrees $deg$ to radians $r$ using the formula
  $$r = \frac{deg}{180} \cdot \pi$$  

Your output should look something like the following.  

\begin{minted}{text}
Location Distance
========================
Origin:      (41.948300, -87.655600)
Destination: (40.820600, -96.705600)
Air distance is 764.990931 kms
\end{minted}


\section*{Instructions}

\begin{itemize}
  \item You are encouraged to collaborate any number of students 
  before, during, and after your scheduled hack session.  
  \item Design at least 3 test cases \emph{before} you begin
  designing or implementing your program.  Test cases are 
  input-output pairs that are known to be correct using means
  other than your program.
  \item Include the name(s) of everyone who worked together on
  this activity in your source file's header.
  \item Place your code in a \mintinline{java}{main()} method in 
    a source file named \mintinline{text}{AirDistance.java} and 
    turn it in via webhandin.  Make sure that it runs and executes 
    correctly in the webgrader. Each individual
    student will need to hand in their own copy and will receive their
    own individual grade.
  \item Remember to RTM (Read The Manual) on Java's 
    \mintinline{java}{Math} class/library to see which method(s) 
    you may find useful and how to use them.
\end{itemize}
  


\end{document}
