\documentclass[12pt]{scrartcl}

\input{preamble}

\makeatletter
\title{Hack 3.0}\let\Title\@title
\subtitle{Computer Science I - Honors\\
{\small
\vskip1cm
Department of Computer Science \& Engineering \\
University of Nebraska--Lincoln}
\vskip-1cm}
%\author{Dr.\ Chris Bourke}
\date{~}
\makeatother

\begin{document}

\maketitle

\hrule

\input{instructions.tex} 

\section*{Problem Statement}

A cell phone broadband provider sells monthly data plans to its
customers.  Each data plan is for 30 days and each plan gives
customers a certain number of Gigabytes (GB) which must be used 
each month or they are lost (no ``rollover'').  The provider wants
to help customers understand if they are using their monthly data
too quickly or if they can afford to use more.

In this exercise, you will write an application for the company
to help customers track their mobile data usage.  Write a program
that reads the following pieces of data as \emph{command line arguments}.
\begin{itemize}
  \item Number of GB in the plan per 30 day period
  \item The current day in the 30 day period (in the range 1, first day, 
  30 for the last day)
  \item The total number of GB used so far
\end{itemize}
The program should then compute whether the customer is over, 
under, or right on the \emph{average daily usage} of their plan.  
It should also inform them of how many GB are left and how many, 
on average, they can use per day for the rest of the 30 day period.  
Of course, if they've run out of data, it should inform them of that 
too.

For example, if the user enters $15, 10, 13$ for each piece of data
respectively, your program should print out something similar to 
the following.

\begin{minted}{text}
10 days used, 20 days remaining
Average daily use: 1.3 GB/day

You are EXCEEDING your average daily use (0.50 GB/day).
Continuing this high usage, you'll exceed your data plan by
24 GB.

To stay below your data plan, use no more than 0.1 GB/day.
\end{minted}

If the user is under their average daily use, a different
message should be presented.  

\section*{Instructions}

\begin{itemize}
  \item You are encouraged to collaborate any number of students 
  before, during, and after your scheduled hack session.  
  \item Design at least 3 test cases \emph{before} you begin
  designing or implementing your program.  Test cases are 
  input-output pairs that are known to be correct using means
  other than your program.
  \item Include the name(s) of everyone who worked together on
  this activity in your source file's header.
  \item Place your code in a \mintinline{java}{main()} method in a 
    source file named \mintinline{text}{DataPlan.java} and turn it 
    in via webhandin.  Make sure that
    it runs and executes correctly in the webgrader. Each individual
    student will need to hand in their own copy and will receive their
    own individual grade.
\end{itemize}
  


\end{document}
