\documentclass[12pt]{scrartcl}

\input{preamble}

\makeatletter
\title{Hack 8.0}\let\Title\@title
\subtitle{Strings \& String Processing\\
Computer Science I -- Java\\
{\small
\vskip1cm
Department of Computer Science \& Engineering \\
University of Nebraska--Lincoln}
\vskip-1cm}
%\author{Dr.\ Chris Bourke}
\date{~}
\makeatother

\begin{document}

\maketitle

\hrule

\input{instructions.tex}

\section*{Exercises}

To get more practice working with strings, you will write several 
methods that involve operations on strings.  In particular, implement
the following methods with the described behavior.  You \emph{must}
use the given signatures.

\begin{enumerate}

  \item Write a method that replaces instances of a given character 
  with a different character in a string.
  
  \mintinline{java}{public static String replaceChar(String s, char oldChar, char newChar)}
  
  This method will replace any instance of the character stored in 
  \mintinline{java}{oldChar} with the character stored in \mintinline{java}{newChar} 
  in the string \mintinline{java}{s}.  

  \item Write a method that takes a string and removes all instances 
  of a certain character from it.
  
  \mintinline{java}{public static String removeChar(String s, char c)}

  \item Write a method that takes a string and splits it up to a 
  \emph{list} of strings.  The split will be length-based: the function 
  will take an integer $n$ and will split the given string up into 
  strings of length $n$.  It is possible that the last string will not 
  be of length $n$.  Throw an \mintinline{java}{IllegalArgumentException} for any invalid inputs.
  
  \mintinline{java}{public static List<String> lengthSplit(String s, int n)}

  For example, if we pass \mintinline{java}{"Hello World, how are you?"} with 
  $n = 3$ then it 
  should return a list of size 9 containing the strings \mintinline{java}{"Hel"}, \mintinline{java}{"lo "}, \mintinline{java}{"Wor"}, 
\mintinline{java}{"ld,"}, \mintinline{java}{" ho"}, \mintinline{java}{"w a"}, \mintinline{java}{"re "}, \mintinline{java}{"you"}, \mintinline{java}{"?"}

\end{enumerate}

\section*{Instructions}

\begin{itemize}

  \item Place all your methods into a source file 
  named \mintinline{text}{StringUtils.java} along with proper documentation.
  
  \item In addition, create a main test driver program called
  \mintinline{text}{StringTester.java} that demonstrates at least 3 cases 
  per function to verify their output.  Hand in your tester.
  
  \item You are encouraged to collaborate with any number of students 
  before, during, and after your scheduled hack session.  

  \item You may (in fact are encouraged) to define any additional
  ``helper'' methods that may help you.
  
  \item Include the name(s) of everyone who worked together on
  this activity in your source file's header.

  \item Turn in all of your files via webhandin, making sure that 
  it runs and executes correctly in the webgrader.  Each individual 
  student will need to hand in their own copy and will receive 
  their own individual grade.

\end{itemize}  


\end{document}
