\documentclass[12pt]{scrartcl}

\input{preamble}

\makeatletter
\title{Hack 10.0}\let\Title\@title
\subtitle{Computer Science I\\
File I/O\\
{\small
\vskip1cm
Department of Computer Science \& Engineering \\
University of Nebraska--Lincoln}
\vskip-2cm}
%\author{Dr.\ Chris Bourke}
\date{~}
\makeatother

\begin{document}

\maketitle

\hrule

\input{instructions.tex}

Correctness:
\begin{itemize}
  \item 5 points for each function
  \item 1 point for error handling
  \item 5 points for protein program
\end{itemize}

\section*{Exercises}

To get more practice working with files, you will write several 
functions that involve operations on files.  In particular, implement
the following functions.

\begin{enumerate}

  \item Write a function that, given a file path/name as a string opens
  the file and returns its entire contents as a single string.  Any endline
  characters should \emph{be preserved}.
  
  \mintinline{c}{char *getFileContents(const char *filePath);}

  \item Write a function that, given a file path/name as a string opens
  the file and returns the contents of the file as an array of strings.
  Each element in the array should correspond to a line in the file.
  Any end line character should be \emph{chomped out} and not included.
  The size of the resulting array of strings needs to be communicated to the calling
  function using the pass-by-reference \mintinline{c}{numLines} parameter
  (it is \emph{not} input).

  \mintinline{c}{char **getFileLines(const char *filePath, int *numLines);}

\end{enumerate}

\subsection*{Protein Translation}

DNA is a molecule that encodes genetic information.  A DNA sequence is 
a string of nucleotides represented as letters A, T, C, and G (representing
the nucleobases adenine, thymine, cytosine, and guanine respectively).  
Protein sequencing in an organism consists of a two step process.  First 
the DNA is translated into RNA by replacing each thymine nucleotide with 
uracil (U).  Then, the RNA sequence is translated into a protein (a sequence
of amino acids) according to the following rules.

The RNA sequence is processed 3 bases at a time called a \emph{codon}.  
Each codon is translated into a single amino acid according to known 
encoding rules.  There are 20 such amino acids, each represented by a 
single letter in 
 $$(A,C,D,E,F,G,H,I,K,L,M,N,P,Q,R,S,T,V,W,Y)$$
Because there are $4^3 = 64$ possible codons but only 20 amino acids,
some codons translate to the same amino acid.

The rules for translating trigrams are complex, but we've simplified
the process by providing a utility function, \mintinline{c}{rnaToProtein}
which takes an RNA codon (as a string) and returns its protein (as a 
single \mintinline{c}{char}).  If you provide it an invalid sequence, it
will return \mintinline{text}{\0} the null character.

In addition, the trigrams UAA, UAG, and UGA are special markers that 
indicate a (premature) end to the protein sequencing (there may be 
additional nucleotides left in the RNA sequence, but they are ignored 
and the translation ends).  The function we've provided will
return a lower-case \mintinline{c}{x} character for any of these three 
trigrams.

As an example, suppose we start with the DNA sequence $AAATTCCGCGTACCC$; 
it would be encoded into RNA as $AAAUUCCGCGUACCC$; and into an amino 
acid sequence $KFRVP$.

You will write a program that takes two command line arguments.  The
first is an input file containing a DNA sequence and the second is the
name of the output file in which you'll place the translated protein
sequence.  As an example, your program should be executable from the 
command line as:

\mintinline{text}{~>./a.out dnaInputFile.txt protein.txt}

The input file \emph{may} contain irrelevant whitespace characters to
avoid very long lines.  You will need to \emph{ignore} any whitespace
characters when you process the data.  

Place all your code in a file named \mintinline{text}{proteinTranslator.c}.

\section*{Instructions}

\begin{itemize}

  \item For the exercises, place all your function prototypes into a file 
  named \mintinline{text}{file_utils.h} and and their definitions in a
  file named \mintinline{text}{file_utils.c}.  In addition, you'll want
  to create a main test driver program that demonstrates at least 3 cases 
  per function to verify their output.  You need not hand it in, however.
  
  \item Code for the \mintinline{c}{rnaToProtein} function as well as 
  a demonstration on how to use it has been provided in the following repo:

  \url{https://github.com/cbourke/CSCE155-Hack10.0}

  However, you only need to handin \mintinline{text}{proteinTranslator.c}
  (and anything else that you may find helpful).  Do \emph{not} make changes
  to the provided files since you won't be able to hand them in (the grading
  script provides them for you).
  
  \item \textbf{Hint}: Code reuse is a Very Good Thing.  Your protein program
  can use your file utility functions, but also: feel free to include
  any additional functions you may have written before in the 
  \mintinline{text}{file_utils.h} and \mintinline{text}{file_utils.c} files
  and use them in your protein translator program.

  \item You are encouraged to collaborate any number of students 
  before, during, and after your scheduled hack session.  

  \item You may (in fact are encouraged) to define any additional
  ``helper'' functions that may help you.

  \item Include the name(s) of everyone who worked together on
  this activity in your source file's header.

  \item Turn in all of your files via webhandin, making sure that 
  it runs and executes correctly in the webgrader.  Each individual 
  student will need to hand in their own copy and will receive 
  their own individual grade.
\end{itemize}  


\end{document}
