\documentclass[12pt]{scrartcl}

\input{preamble}

\makeatletter
\title{Hack 12.0}\let\Title\@title
\subtitle{Computer Science I\\
Recursion \& Function Pointers\\
{\small
\vskip1cm
Department of Computer Science \& Engineering \\
University of Nebraska--Lincoln}
\vskip-3cm}
%\author{Dr.\ Chris Bourke}
\date{~}
\makeatother

\begin{document}

\maketitle

\hrule

\section*{Introduction}

Hack session activities are small weekly programming assignments intended
to get you started on full programming assignments.  Collaboration is allowed
and, in fact, \emph{highly encouraged}.  You may start on the activity before
your hack session, but during the hack session you must either be actively 
working on this activity or \emph{helping others} work on the activity.
You are graded using the same rubric as assignments so documentation, style, 
design and correctness are all important.  This activity is \textbf{due 
at 23:59:59 on the Friday} in the week in which it is assigned according 
to the CSE system clock.

\section*{Problem Statement}

TODO

\section*{Instructions}

\begin{itemize}

  \item Place all of your function definitions in a source file named 
  \mintinline{text}{airport.c} and hand it in with your header file, 
  \mintinline{text}{airport.h}.  You may add any utility functions you
  wish but you must \emph{not} change any of the signatures of the required
  functions.
  
  \item In addition, you must create a main test driver program that 
  demonstrates at least 3 cases per function.  Name this file 
  \mintinline{text}{airportTester.c} and hand it in.

  \item You are encouraged to collaborate any number of students 
  before, during, and after your scheduled hack session.  

  \item You may (in fact are encouraged) to define any additional
  ``helper'' functions that may help you.

  \item Include the name(s) of everyone who worked together on
  this activity in your source file's header.

  \item Turn in all of your files via webhandin, making sure that 
  it runs and executes correctly in the webgrader.  Each individual 
  student will need to hand in their own copy and will receive 
  their own individual grade.
\end{itemize}  


\end{document}
